Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-08 article.tex

The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple regions describing the unique varietals and qualities of wine produced there. While a great deal has been done regarding regional properties and traits, there has been little statistical insight into how regions differ; this has been due to a lack of cross-regional and in-depth data sources   (Keith Jones, 2002; Knight et al., 2019). In this study we use Classification Trees to compare regional differences and how they relate to sustainable practices and grape quality.
The site of a vineyard predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality. Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.

>>>>

The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \autocite{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
\newline
A vineyard's region predetermines several physical parameters, such as: climate, geology and soil; making location a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. 
%
%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
% What the hell is a regional strategy
% And how do you define, or know what trategy each region is using?
%
Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.

% This does not really address what the methods are - aside from classisifcation trees in the most vague sense.
% What are the results briefly? why should someone read this article?
% What is interesting - what will be discussed in the article with regard to these results? What makes me want to read the article?
% And what is the take away point of the article? If I cant be bothered to read this article, what piece of knowledge can you leave mewiwth that I could recommend the article to someone else with?
